A Data-Driven Framework for Neural Field Modelling

### 2010-10-30 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure10

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure10.pdf}
\end{center}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:Figure10}
\end{figure*}

>>>>

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure10.pdf}
\end{center}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{a}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{b}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{c}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:Figure10}
\end{figure*}
